---
title: "Problem_set_2"
author: "May"
date: "10/30/2022"
output: html_document
---

#This is problem set 2!

First, lets clear R's brain, and add some packages
```{r}
rm(list=ls())
library(dplyr)
library(here)
library(ggplot2)
library(tidyr) #adding this to help me remove nas
```

Now, lets bring in the Halloween_data_PS2.csv
We'll call it Halloween
```{r}
Halloween <- read.csv(here("Data", "Halloween_data_PS2.csv") , stringsAsFactors = TRUE) # make the variables factors
View(Halloween) #to view the dataset
```

Now lets look at the names of the variables
```{r}
names(Halloween)
```
Now lets show the data with all rows minus "age"
```{r}
select(Halloween, -age)
```

Now lets look for unique data in the set
```{r}
unique(Halloween)
```
I'm not sure what these last several lines of code have done for you. In terms of becoming familiar with the data, they are ok, but they haven't shown you any potential issues within each variable, such as incorrectly formatted text within a column.


```{r}
Halloween$Costume <- tolower(Halloween$Costume) #this makes all values in column all lowercase
Halloween$Type <- tolower(Halloween$Type)
Halloween$Costume <- trimws(Halloween$Costume)# this trims space before or after values
Halloween$Type <- trimws(Halloween$Type)
Halloween <- slice(Halloween , -c(4, 12, 29, 30)) #to slice out all rows with NA's

glimpse(Halloween)
```

I don't agree with your choice to simply delete rows because they have NAS - doing so is throwing away data. You can deal with the NA's individually and keep some of the data. See the key for details.


```{r}
totals <- Halloween %>%
group_by(Costume, Type) %>%
summarise(totals.mean_candy = mean(candy_pieces), totals.mean_age = mean(age)) #finding mean of both variables within the group
View(totals)
  
```



Now lets make a scatterplot of the number of pieces of candy taken from children 10 and under
```{r}
ggplot(totals, aes(x = totals.mean_age, y = totals.mean_candy, colour = Type)) + geom_point(size =2)+
xlab("Mean age of kids (years)") +
ylab("Mean number pieces taken")
```

Now lets create a histogram for children in not scary costumes under the age of ten
```{r}
Children <-filter(Halloween, Type == "not scary" | age <= 10) #specifies children Type not scary and age less than or equal to 10 
ggplot(Children, aes(x = age)) + geom_histogram(bins = 4)+
xlab("Age of Child")+
ylab("Number")
```

Now let's create a box plot
```{r}
ggplot(Halloween, aes(x = age, y = Costume)) + geom_boxplot() + facet_wrap(~Type)+
xlab("Child age (years)")+
  ylab("Costume choice")
```

Save and commit
