---
title: "Problem_set_2"
author: "May"
date: "10/30/2022"
output: html_document
---

#This is problem set 2!

First, lets clear R's brain, and add some packages
```{r}
rm(list=ls())
library(dplyr)
library(here)
library(ggplot2)
library(tidyr) #adding this to help me remove nas
```

Now, lets bring in the Halloween_data_PS2.csv
We'll call it Halloween
```{r}
Halloween <- read.csv(here("Data", "Halloween_data_PS2.csv") , stringsAsFactors = TRUE) # make the variables factors
View(Halloween) #to view the dataset
```

Now lets look at the names of the variables
```{r}
names(Halloween)
```
Now lets show the data with all rows minus "age"
```{r}
select(Halloween, -age)
```

Now lets look for unique data in the set
```{r}
unique(Halloween)
```

```{r}
Halloween$Costume <- tolower(Halloween$Costume) #this makes all values in column all lowercase
Halloween$Type <- tolower(Halloween$Type)
Halloween$Costume <- trimws(Halloween$Costume)# this trims space before or after values
Halloween$Type <- trimws(Halloween$Type)
Halloween <- slice(Halloween , -c(4, 12, 29, 30)) #to slice out all rows with NA's

glimpse(Halloween)
```

```{r}
totals <- Halloween %>%
group_by(Costume, Type) %>%
summarise(totals.mean_candy = mean(candy_pieces), totals.mean_age = mean(age)) #finding mean of both variables within the group
View(totals)
  
```



Now lets make a scatterplot of the number of pieces of candy taken from children 10 and under
```{r}
ggplot(totals, aes(x = totals.mean_age, y = totals.mean_candy, colour = Type)) + geom_point(size =2)+
xlab("Mean age of kids (years)") +
ylab("Mean number pieces taken")
```

Now lets create a histogram for children in not scary costumes under the age of ten
```{r}
Children <-filter(Halloween, Type == "not scary" | age <= 10) #specifies children Type not scary and age less than or equal to 10 
ggplot(Children, aes(x = age)) + geom_histogram(bins = 4)+
xlab("Age of Child")+
ylab("Number")
```

Now let's create a box plot
```{r}
ggplot(Halloween, aes(x = age, y = Costume)) + geom_boxplot() + facet_wrap(~Type)+
xlab("Child age (years)")+
  ylab("Costume choice")
```

Save and commit
